\addcontentsline{toc}{section}{References}

\begin{thebibliography}{3}
\bibitem{0} GelferT, A. Fake News: A Definition.
    Informal Logic, Vol. 38, No.1 (2018), pp. 84-117.
\bibitem{1} Rubin, Victoria \& Chen, Yimin \& Conroy, Nadia. (2015).
    Deception Detection for News: Three Types of Fakes.
\bibitem{2} S. I. Manzoor, J. Singla and Nikita, "Fake News Detection Using Machine Learning approaches: A systematic Review," 2019 3rd International Conference on Trends in Electronics and Informatics (ICOEI), Tirunelveli, India, 2019, pp.
    230-234, doi: 10.1109/ICOEI.2019.8862770.
\bibitem{3} Parikh, S. B., \& Atrey, P. K. (2018, April).
    Media-Rich Fake News Detection: A Survey.
    In 2018 IEEE Conference on Multimedia Information Processing and Retrieval (MIPR) (pp. 436--441).
    IEEE\@.
\bibitem{4} Conroy, N. J., Rubin, V. L., \& Chen, Y. (2015, November).
    Automatic deception detection: Methods for finding fake news.
    In Proceedings of the 78th ASIS\&T Annual Meeting: Information Science with Impact: Research in and for the Community (p. 82).
    American Society for Information Science.
\bibitem{5} Della Vedova, M. L., Tacchini, E., Moret, S., Ballarin, G., DiPierro, M., \& de Alfaro, L. (2018, May).
    Automatic Online Fake News Detection Combining Content and Social Signals.
    In 20182018--22   Conference of Open Innovations Association (FRUCT) (pp. 272-279).
    IEEE.
\bibitem{6} Tacchini, E., Ballarin, G., Della Vedova, M. L., Moret, S., \& de Alfaro, L. (2017).
    Some like it hoax: Automated fake news detection in social networks.
    arXiv preprint arXiv:1704.07506.
\bibitem{7} Khan, Junaed Younus \& Khondaker, Md. Tawkat Islam \& Iqbal, Anindya \& Afroz, Sadia. (2019).
    A Benchmark Study on Machine Learning Methods for Fake News Detection.
\bibitem{8} Ahmed, Alim \& Aljabouh, Ayman \& Donepudi, Praveen \& Choi, Myung. (2021).
    Detecting Fake News Using Machine Learning : A Systematic Literature Review.
\bibitem{9} K. Shu, A. Sliva, S. Wang, J. Tang, and H. Liu, "Fake news detection on social media: A data mining perspective", ACM SIGKDD Explorations Newsletter, vol.
    19, no. 1, pp. 22\textendash36, 2017.
\end{thebibliography}
